Process-based phenotypes: an application to the Cellular Phenotype Ontology

### 2011-11-23 paper/drinking.tex

\documentclass{bioinfo}
\copyrightyear{2005}
\pubyear{2005}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{multirow}
\usepackage{pifont}
% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage[utf8]{inputenc} %unicode support
\urlstyle{rm}
\usepackage{natbib}
\renewcommand{\cite}{\citep}
\usepackage{amsmath}
\usepackage{amssymb}

@@

@@

\section{Methods}
\subsection{Formal ontology}
The ontology as an approach to semantic standardisation was proposed
more than a decade ago and since then has become the dominant
methodology used to semantically categorise phenodeviance.  The
biomedical research community has invested considerable amount of
effort and resources in the development and establishment of
ontologies that are becoming increasingly successful as information
management and integration tools in many disparate scientific fields
allowing interoperability and semantic information processing between
diverse biomedical resources and domains.

@@

The second common type of abnormality are abnormalities based on
process participants in relation to the duration of the process. These
include all kinds of {\em rates} such as {\em mass flow rate}, {\em
  energy flow rate} and {\em velocity} (the rate of change of
position). In each of these cases, an object participates in a process
and a quality (or change of quality) of that object throughout the
duration of the process is considered to form a new quality. If the
process has participants that are distinguished into {\em inputs} and
{\em outputs}, then a recurring pattern is that the amount of inputs
or outputs that participate in the process can be {\em increased} or
{\em decreased}. For example, an {\em Increased rate of cytoplasmic
  streaming} is defined as

@@

A second kind of regulatory abnormalities is related to the {\em
  onset} of a process. With respect to a reference process, a
particular kind of process may be {\em delayed} ({\tt PATO:0000502})
or {\em premature} ({\tt PATO:0000694}). For example, {\em Delayed
  apoptosis} refers to an abnormality of the {\em Regulation of
  apoptosis} in which apoptosis is induced later than normal.  We use
the PATO quality {\em onset} ({\tt PATO:...}) and its children {\em
  delayed} and {\em premature} to define these types of regulatory
abnormality.

Finally, a third kind of regulatory abnormality refers to abnormal
rates with respect to a participant of the process that is being
regulated.

@@

\section{Conclusion}

@@

% % %%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Acknowledgements}
% The authors declare that they have no competing interests.

@@

\bibliographystyle{plain} % Style BST file
\bibliography{../bibtex/lc.bib}

>>>>

\documentclass{bioinfo}
\usepackage{setspace}

\copyrightyear{2005}
\pubyear{2005}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{multirow}
\usepackage{pifont}
% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage[utf8]{inputenc} %unicode support
\urlstyle{rm}
\usepackage{natbib}
\renewcommand{\cite}{\citep}
\usepackage{amsmath}
\usepackage{amssymb}

@@

{\bf Keywords:} cell phenotype, process, ontology, Semantic Web

@@

\section{Materials and Methods}
\subsection{Formal ontology}
The ontology as an approach to semantic standardisation was proposed
more than a decade ago and since then has become the dominant
methodology used to semantically categorise phenodeviance.  The
biomedical research community has invested considerable amount of
effort and resources in the development and establishment of
ontologies that are becoming increasingly successful as information
management and integration tools in many disparate scientific fields
allowing interoperability and semantic information processing between
diverse biomedical resources and domains.

@@

The second common type of abnormality are abnormalities based on
process participants in relation to the duration of the process. These
include all kinds of {\em rates} such as {\em mass flow rate}, {\em
  energy flow rate} and {\em velocity} (the rate of change of
position). In each of these cases, an object participates in a process
and a quality (or change of quality) of that object throughout the
duration of the process is considered to form a new quality. If the
process has participants that are distinguished into {\em inputs} and
{\em outputs}, then a recurring pattern is that the amount of inputs
or outputs that participate in the process can be {\em increased} or
{\em decreased}. For example, an {\em Increased rate of cytoplasmic
  streaming} is defined as...

@@

A second kind of regulatory abnormalities is related to the {\em
  onset} of a process. With respect to a reference process, a
particular kind of process may be {\em delayed} ({\tt PATO:0000502})
or {\em premature} ({\tt PATO:0000694}). For example, {\em Delayed
  apoptosis} refers to an abnormality of the {\em Regulation of
  apoptosis} in which apoptosis is induced later than normal.  We use
the PATO quality {\em onset} ({\tt PATO:...}) and its children {\em
  delayed} and {\em premature} to define these types of regulatory
abnormality. Similarly, we use PATO's {\em offset ({\tt PATO:...})
  quality and its children to characterize regulatory abnormalities in
  which a process ends prematurely or too late.

Finally, a third kind of regulatory abnormality refers to abnormal
rates with respect to a participant of the process that is being
regulated. For example, a cytoplasmic flow rate can

@@

\subsection{Conclusion}

\section{Acknowledgements}

@@

% % %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The authors declare that they have no competing interests.

@@

\bibliographystyle{plain} % Style BST file
\bibliography{lc}
